Paradigms in Physics 2.0

### 2017-06-27 paper.tex
count facutly members

\paragraph{New faculty}
At this stage, (XX) of our faculty was not present during the orignal
Paradigms effort.  Many of the newer faculty have only a superficial
undertanding of our course structure.  This poses a challenge when
these professors teach courses that are closely intertwined with one
another.

>>>>

\paragraph{New faculty}
% Corinne, Henri, David McI, Janet, Tom = 5

% David R, Ethan, Oksana, Bo, Guenter, Weihong, Matt, Yun-Shik, Heidi,
% Liz, Davide = 11
Only 5 of our 16 current tenure-line faculty were involved in the
orignal Paradigms effort.  Some of the newest faculty have only a
superficial undertanding of our course structure.  This poses a
challenge when these professors teach courses that are closely
intertwined with one another.
